# Coursera Reproducible Research Week2 Assignment
  
## Load libraries
Load necessary packages.
```{r packages, echo=TRUE}
library(dplyr)
library(ggplot2)
```
  
## Load and clean the data
This is the data.
```{r read_data, echo=TRUE}
data <- read.csv("activity.csv")
str(data)
```
The data variable is a factor.
Change them into date format.
```{r clean_data, echo=TRUE}
data <- data %>% 
	mutate(date=as.Date(date, "%Y-%m-%d"))
```
  
## Total number of steps taken per day
Calculate the total number of steps taken per day
and make a histogram.
```{r total_hist, echo=TRUE}
data %>% group_by(date) %>% 
	summarise(steps = sum(steps, na.rm=TRUE)) %>%
	ggplot(aes(x=steps)) + 
	geom_histogram(bins=30) +
	labs(title="The total number of steps per day") 
```

Calculate the mean and median of the
total number of steps taken per day
```{r total_me, echo=TRUE}
data %>% group_by(date) %>%
	summarise(mean_steps = mean(steps, na.rm=TRUE),
		median_steps = median(steps, na.rm=TRUE)) %>%
	summary
```
  
## Average daily activity pattern
Make a time series plot of the 5 minute interval
and the average number of steps taken
```{r daily_line, echo=TRUE}
data %>% group_by(interval) %>%
	summarise(ave_steps = mean(steps, na.rm=TRUE)) %>%
	ggplot(aes(x=interval, y=ave_steps)) +
	geom_line() +
	labs(title="The average steps of the 5minutes interval")
```

The interval 835 contains the maximum number of steps.
```{r daily_head, echo=TRUE}
data %>% group_by(interval) %>%
	summarise(ave_steps = mean(steps, na.rm=TRUE)) %>%
	arrange(desc(ave_steps)) %>% head
```
  
## Impute missing values
Calculate the total number of missing values in the dataset.
The step variable has 2303 NAs in 17568 rows.
```{r missing, echo=TRUE}
summary(data)
dim(data)
```
Fill in all of the missing values using the mean
for that 5-minute interval and create a new dataset.
```{r missing_fill, echo=TRUE}
newData <- data %>% group_by(interval) %>%
	mutate(steps=ifelse(is.na(steps), 
		mean(steps, na.rm=TRUE),steps)) %>%
	ungroup
```
Make a histogram and calculate the mean and median like the
first assignment. Imputing missing data doesn't impact the
mean much but changed median of steps. 
Not the histogram is highly right skewed.
```{r full_hist, echo=TRUE}
newData %>% group_by(date) %>%
	ggplot(aes(x=steps)) +
	geom_histogram(bins=30) +
	labs(title="The total number of steps per day2") 
```
```{r full_me, echo=TRUE}
newData %>% group_by(date) %>%
	summarise(mean_steps = mean(steps),
		median_steps = median(steps)) %>%
	summary
```
  
## The differences between weekdays and weekends
add a new factor variable indicating whether a given
date is a weekday or weekend day.
```{r week, echo=TRUE}
newData <- newData %>%
	mutate(week=ifelse(weekdays(date)%in%c("Sunday","Saturday"),
			"weekend", "weekday")) %>%
	mutate(week=as.factor(week))
```

Make a panel plot containing a time series plot of the interval
and the average number ov steps taken
```{r week_lines, echo=TRUE}
newData %>% group_by(interval, week) %>%
	summarise(ave_steps = mean(steps)) %>%
	ggplot(aes(x=interval, y=ave_steps)) +
	geom_line(aes(color=week)) +
	labs(title="The average steps of the 5minutes interval2")
```